### 2015-05-30 writing/SNLI paper/entailment_eval.tex
Paper update.

% Insights 1: lexicalization helps a bunch
It is interesting to note the substantial jump in accuracy from using
  lexicalized features, and even from using the relatively sparse
  cross-bigram features.
In fact, the addition of these features alone allow the classifier to
  outperform the EOP models -- this is in some sense unsurprising:
  the EOP systems have been tuned on relatively small corpora
  ($\sim$1600 examples), whereas a classifier trained on our corpus can make use of
  over two orders of magnitude more data.
  \todo{Use curve to justify large size of corpus.}

@@

@@

We attempted to apply this same transfer evaluation technique to the RTE-3 challenge dataset, but found that the small size of the training set (800 examples) did not allow our model to adapt to the

@@

Fig.~\reffig{bowlearncurve} shows a learning curve for the LSTM and the lexicalized and unlexicalized feature-based models. Here, we observe further confirmation that supervised neural network models like our LSTM-based model are only competitive 
% describe intersection
% promising with more data
% useful resource in the development of more sophisticated SE models

@@

% Insights 2: the learning curve for the unlexicalized classifier is sad
Setting aside the neural network model, were surprised at how quickly
the lexicalized classifier outperforms its
  unlexicalized counterpart (see \reffig{bowlearncurve}).
With only 100 training examples, the cross-bigram classifier is already
  outperforming its unlexicalized counterpart.
Empirically we notice that the top weighted features for the classifier
  trained on 100 examples tend to be high precision entailments;
  e.g.,
  \textit{playing} $\rightarrow$ \textit{outside}
  (most scenes are outdoors), or \textit{a banana} $\rightarrow$
  \textit{person eating}.
If relatively few spurious entailments get high weight -- as it appears
  is the case -- then it makes sense that when these do fire they
  provide some boost in accuracy.

>>>>

% Insights 1: lexicalization helps a bunch
It is interesting to note the substantial jump in accuracy from using
  lexicalized features, and even from using the relatively sparse
  cross-bigram features.
In fact, the addition of these features alone allow the classifier to
  outperform the EOP models -- this is in some sense unsurprising:
  the EOP systems have been tuned on relatively small corpora
  ($\sim$1600 examples), whereas a classifier trained on our corpus can make use of
  over two orders of magnitude more data.

@@

The results are shown in Table~\ref{tab:nnresults}. The sum of words model performed slightly worse than the fundamentially similar lexicalized classifier---while the sum of words model is able to use pretrained word embeddings to better handle rare words, it lacks even the rudimentary sensitivity to word order that the lexicalized model's bigram features provide. Of the two RNN models, our observations find that the more robust ability to learn long-term dependencies serves it well, giving it the strongest performance of any model we tested.

@@

\todo{Comparison with other models on 2?3?-way SICK}

We attempted to apply this same transfer evaluation technique to the RTE-3 challenge dataset, but found that the small size of the training set (800 examples) did not allow the model to adapt to the unfamiliar genre of text use in that corpus, such that neither our transfer model nor our randomly initialized model reached competitive performance.

@@

Fig.~\reffig{bowlearncurve} shows a learning curve for the LSTM and the lexicalized and unlexicalized feature-based models. This learning curve shows that the large size of the corpus is crucial to both the LSTM and the lexicalized model, and suggests that additional data would yield still better performance. It is also worth noting that though the LSTM and the lexicalized model show similar performance when trained on the data we present here, the steeper slope for the LSTM suggests that its ability to learn arbitrarily structured representations of sentence meaning would give it an advantage over the more constrained lexicalized model on still larger datasets.

% useful resource in the development of more sophisticated SE models

@@

% Insights 2: the learning curve for the unlexicalized classifier is sad
We were struck by how quickly the lexicalized classifier outperforms its unlexicalized counterpart.
With only 100 training examples, the cross-bigram classifier is already outperforming its unlexicalized counterpart.
Empirically we notice that the top weighted features for the classifier
  trained on 100 examples tend to be high precision entailments;
  e.g.,
  \textit{playing} $\rightarrow$ \textit{outside}
  (most scenes are outdoors), or \textit{a banana} $\rightarrow$
  \textit{person eating}.
If relatively few spurious entailments get high weight -- as it appears
  is the case -- then it makes sense that when these do fire they
  provide some boost in accuracy.
